Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Extend TBD note
Whitespace changes

To test properties, we also uses GHCi.
Each property is enclosed with
the ``\verb|quickCheck (|'' and ``\verb|)|'' string
and GHCi evaluates it.
Success or failures is decided according to result string from GHCi.

@@

    Below is the schematic algorithm, from my original mail to kazu:
\end{quote}

>>>>

To test properties, we also use GHCi.  Each property is enclosed
within ``\verb|quickCheck (|'' and ``\verb|)|'' string and GHCi
evaluates it.  Success or failures is decided according to result
string from GHCi.

@@

    Below is the schematic algorithm, from my original mail to kazu.
    Can we somehow get rid of haskell-src, and hint, and only describe
    the algorithm?
\end{quote}
